Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-07 paper/main.tex
Estimate of double SHA-256 in supercop

>>>>

\section{\ac{SUPERCOP} results}
We see in tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-LAFS uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume that cycles/bytes is linear from 8 byte to 64 byte, we get the
following estimate for the speed of hashing 32 bytes:

$$179.62 - \frac{179.62 - 38.12}{64 - 8} * (32-8)= 118.98 (Cycles/byte)$$

We can then estimate the result of each message by the following formula:
$$\frac{median * size + 118.98*32}{size} = SHA256d estimate$$

\input{tables/supercop_sha256d}
Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see is that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a filesystem, most files processed
will have be larger than the file sizes estimated here. Even though not all
hashing operations done in Tahoe are related to the file size, we expect that
only BLAKE, \ac{BMW}, Luffa, Shabal and SIMD will be able to outperform double
\ac{SHA}-256.
